Solution Outline

### 2020-04-16 documentation/systemModel/formalized_work.tex
just some small changes while investigating impact of cross terms

>>>>

\item
*TO DISCUSS If the phases cancel out, then they cannot influence the final AED or the expected value. Does this mean that controlling these phases is not beneficial in the asymptotic limit?
Note these terms might affect the AED of the cross terms in the polynomial but we hypothesis that these cancel out anyways.
